### 2021-04-14 Paper/Main.tex

\begin{document}
\section{Introduction and Motivation}
Asset pricing has a long history of models and theories governing how investor view the prices of assets. Over the last decade investors have become increasingly interested in  factors outside of traditional financial metrics when assessing the possability of an investments returns.Much of this enthusiasm has been based on ESG, Enviomental Social Goverance, investing that considers how firms respond to these factors as potential impetuses for excess performance.  Research from Mckendsey has shown that there is a direct correlation between diversity inside of executive team leadership and company performance. A rising threat of global climate related issues and workplace culture to determine top talent have all become extremely important for company management to consider on the basis of long term performance.

this paper will be broken up into five  sections. \textit{Section \ref{Literature}} will provide a  brief literature review of papers looking abnormal performance around ESG criteria as well as discussion of possible asset pricing models to capture ESG factors in performance. Next in  \textit{ Section \ref{Data}}  I will discuss the data used in this papers as well as the data cleaning process and summary statistics. Following the Data, \textit{Section \ref{Methodology}} will breakdown of the methodology for the paper. Finally, \textit{Section \ref{Results}}  will summarize the results of the regressions, \textit{Section \ref{Robustness}} will check the robustness of the results and \textit{Section \ref{Conclusion}} will provide a conclusion and possible extensions for next steps.

\section{Literature Review}
to account for the ESG factor of a five factor famma french model, the authers used the S\&P ESG index as the high ESG index and the S\&P petroleum index as the low index creating a facotr by subtracting the retunrs from the high ESG portfolio from the low ESG portfolio. \cite{Gregory2020TheGP}
\label{Literature}

@@

>>>>

\begin{document}
\section{Introduction and Motivation}
Asset pricing has a long history of models and theories governing how investors make decisions. Over the last decade, investors have become increasingly interested in factors outside of traditional financial metrics when assessing the possibility of an investment's returns. Much of this enthusiasm has been based on an ESG, Environmental Social Governance, framework. ESG investing considers how firms respond to these factors as potential impetuses for excess performance. This increased attention is especially visible in Morgan Stanley's 2019 survey of the ESG landscape. Morgan Standley  found that 75\% of assessment managers say that "their firm has adopted sustainable investing." Only two years prior, in 2016, just 10\% of surveyed asset managed had adopted sustainable investing, demonstrating the rapid speed of adoption for ESG investing analysis \cite{morgan_stanley_sustainable_2019}. Practitioners have utilized the ESG framework to reduce risk in their investments while also finding abnormal returns.

Global climate change presents a host of possible and sizable financial risks from increased water levels, which could threaten major global cities' safety, including Miami, Honk Konk, and Shanghai, with the potential to displace 100's of millions of people \cite{holder_three-degree_nodate}. Global climate change is also shifting the landscape for global agricultural production as more extreme weather conditions, including droughts, pose problems to the most fundamental building block of economic activity. In addition to risk mitigation, investors look to utilize ESG principle for superior returns. A research report published by McKinsey and Company linked gender diversity on executive teams to higher profitability and superior value creation \cite{mckinsey_diversity}.

In addition to risk investing professionals, ESG investing is appealing to a younger set of investors interested in a plethora of global issues from global climate change to diversity and inclusion in the workplace. A study conducted by Morgan Stanly found that millennials investors were twice as likely as the general investing population to invest in a company with social or environmental goals.

This new wave of investor sentiment has created strong tailwinds for sustainable investment projects. In 2020 alone, fund flows into sustainable funds grew by 51 billion dollars which is up over 100\% for the 2019 fund flow into sustainable investment products of about 21, placing total assets under management in sustainable products at over 250B. Fund flows into sustainable products for 2020 accounted for a little less a quarter of all US mutual fund flow and about one-fifteenth of all ETF fund flow according to morningstar \cite{monring_star_ESG}.

To address the impact of ESG factors on stock preformance, this paper is broken into five sections. \textit{Section \ref{Literature}} will provide a  brief literature review of papers looking at abnormal performance around ESG criteria as well as discussion of asset pricing models to capture ESG factors in performance. Next \textit{ Section \ref{Data}}  will provide a brief discussion of the data used in this paper as well as the data cleaning process and summary statistics. Following the Data, \textit{Section \ref{Methodology}} will breakdown of the methodology for the paper. Finally, \textit{Section \ref{Results}}  will summarize the results of the regressions, \textit{Section \ref{Robustness}} will check the robustness of the results and \textit{Section \ref{Conclusion}} will provide a conclusion and possible extensions for next steps.

\section{Literature Review}
This section will be broke into two components, we will first look at theoretical models for asset purchasing and then we will introduce some of the mythology for introducing a EGS factor into the asset pricing framework.
to account for the ESG factor of a five factor famma french model, the authers used the S\&P ESG index as the high ESG index and the S\&P petroleum index as the low index creating a facotr by subtracting the retunrs from the high ESG portfolio from the low ESG portfolio. \cite{Gregory2020TheGP}
\label{Literature}

@@

*dicuss how we collapse the prolfio from 10 to 2 size
